Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-09-28 paper/main.tex
general makeover until discussion of indv. results

% Titel-Vorgabe < 110 chars incl. spaces
%  jetzt 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Intro: PPA as classic example for an visual area; Methods: fMRI data
studyforrest data set, general linear model; Results: significant clusters in
PPA, RSC, individual results in x of 15 subjects; Conclusions: PPA nicht
exclusively \end{abstract}

\todo[inline]{Intro + Discussion = main text; ca. 3,000 words; some minor
    ``issues'' are in comments and not labeled as to do's}

\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
    wish to use BibTeX to prepare their references should therefore copy the
    reference list from the .bbl file that BibTeX generates and paste it into
    the main manuscript .tex file (and delete the associated
    \textbackslash{}bipliography and \textbackslash{}bibliographystyle
commands)}

@@

\todo[inline]{RSC is not mentioned in the introduction but should (probably)
shortly discussed in the, well discussion; RSC shows up in group results but
mixed results in individual subjects}

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of landscapes,
\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacant
regions of the fusiform gyrus \cite{epstein1998ppa} at the boundary to the anterior lingual gyrus \citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes or landmarks compared to pictures of tools or
faces.
% spatial layout hypothesis
According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

% Wolbers: haptic exploration
In the block design study conducted by \citep{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
    gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma
    keine Connectivität. Interpretation: Es kann keine mental imagery sein;
    ``The scene-related increase in coupling with the PPA was significantly
stronger in multiple clusters in occipital cortex under visual than haptic
stimulation (Figure 2B; Table S2)''}
% Aziz (2008): place related sentences
\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
    Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und
    im Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht
    durch, weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es
verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber
diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
% Aziz' stimuli
To our knowledge only one study \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences. Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
television has a long antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

\todo[inline]{I deleted sentences regarding Aminoff's
    (\citep{aminoff2006parahippocampal, aminoff2013role}) competing ``contextual
associations hypothesis'' because our paradigm does not touch that issue.}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvatage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \citep{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh}.
% Huth (2016)
\todo[inline]{but Huth et al. (2016) implicitly regarding audio-only; but they
do not discuss the PPA; moreover, they do voxel-wise encoding which doesn't say
anything about excitation/inhibition}

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm and test its localization performance of a ``visual
area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare these results to results of a dedicated visual localizer
experiment done with the same participants \citep{sengupta2016extension}.

\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen}

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}
\todo[inline]{current order of subsections might be ``non-canonical''}
\todo[inline]{parts from original studies still detailed; feel free to delete
sentences}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
\todo{this is just loveless listing so far} The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of most important aspects.

@@

\subsection{Naturalistic stimuli annotation}

% stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain an audience and to
capture attention free from any perceptual or behavioral task.
% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
In/for the movie, We annotated different kinds of cinematographic cuts
\citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer in the depicted environment independent from the exact visual content in
the movie frame following the cut.

% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno} by annotating words embedded
in sentences spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that describe the movie's
missing visual content.
% why and how of categories 1
Some categories were created in such a way to reflect the six stimulus
categories used in the visual localizer experiment.
% why and how of categories 2
Some additional categories were created to semantically cluster nouns into
categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
that's basically it}
% categories in detail
Nouns were categorized by the verbal clue they provide about the
cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
its inherent persons (female, female name; male, male name, person), a person's
appearance (face, head; body, bodypart), and a scene's inherent objects (object,
furniture).
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus
segments used during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    categories, annotation rules, and examples (given in English). The category
    \texttt{++} also contains adverbial adjectives and adverbs.}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\todo[inline]{I revised part of motion correction/co-registration but as usually
I am pretty unsure about correctness}
\todo[inline]{Satz zum Downsampling der 7T Daten?}

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
particpant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AO stimulus.

@@

% actual preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every stimulus segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AV analysis, we used all of the original 19
categories of descriptive nouns except \texttt{++}.
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories (see Table \ref{tab:ao-events}) that
served as experimental conditions.
% setting beats other category
Events that fell into one of the two setting-related category but also into
another category were treated as belonging to the setting-related category
(\texttt{se\_new} or \texttt{se\_old}).
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf ich den ganzen
Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuissance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

groom & elements defining geometry of local space & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.

>>>>

% title has to be < 110 chars incl. spaces
%  at the moment 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}

@@

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Intro: PPA as classic example for an visual area; Methods: fMRI data
studyforrest data set, general linear model; Results: significant clusters in
PPA, RSC, individual results in x of 15 subjects; Conclusions: results suggest
generalizability to spoken language and is restricted to processing visual
stimuli exclusively. \end{abstract}

\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
    wish to use BibTeX to prepare their references should therefore copy the
    reference list from the .bbl file that BibTeX generates and paste it into
    the main manuscript .tex file (and delete the associated
    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
commands)}

@@

\todo[inline]{Limit for Intro + Discussion (main text) = ca. 3k words;
intro is about 1k words (with to dos)}

\todo[inline]{RSC is not mentioned in intro anymore but it shows up in group
results (mixed in individual subjects) and therefore could be discussed}

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of landscapes,
\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus \cite{epstein1998ppa} and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes or landmarks compared to pictures of tools or
faces.
% spatial layout hypothesis
According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

% Wolbers: haptic exploration
In the block design study conducted by \citep{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
cortex, and compares connectivity during visual and haptic paradigm: ``The
scene-related increase in coupling with the PPA was significantly stronger in
multiple clusters in occipital cortex under visual than haptic stimulation
(Figure 2B; Table S2)''}
% Aziz (2008): place related sentences
\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und im
Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht durch,
weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es verstanden
habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber diesen
Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
% Aziz' stimuli
To our knowledge only one study \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences. Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
television has a long antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

\todo[inline]{I deleted sentences regarding competing ``contextual associations
    hypothesis'' (\citep{aminoff2006parahippocampal, aminoff2013role}) because
our events/regressors cannot touch that issue; might be interesting during
discussion of anterior/posterior PPA.}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \citep{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh; ``exclusively auditory
stimulation''?}.
% Huth (2016)
\todo[inline]{Huth et al. (2016) implicitly regarding audio-only; but they do
not discuss the PPA; in general, they do voxel-wise encoding which doesn't say
anything about excitation/inhibition}

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm and test its localization performance of a ``visual
area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare these results to results of a dedicated visual localizer
experiment done with the same participants \citep{sengupta2016extension}.

\todo[inline]{maybe insert ``foreshadowing'' of results here?}
\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen}

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}
\todo[inline]{explain as introduction to every step why it woes done}
\todo[inline]{current order of subsections might be ``non-canonical''}
\todo[inline]{parts from original studies might still be too detailed}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},\todo{this is kind of a loveless list}
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of most important aspects.

@@

\subsection{Naturalistic stimuli annotation}
%todo
% stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain an audience and to
capture attention free from any perceptual or behavioral task.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% why and how of categories 1
Some categories were created in such a way to reflect the six stimulus
categories used in the visual localizer experiment.
% why and how of categories 2
Some additional categories were created to semantically cluster nouns into
categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
that's basically it}
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% problem with hierarchical categories
\todo[inline]{put stuff regarding hierarchical categories and heterogeneity
here; counts in table show the counts of just the primary category; settings
changes often (30-60 \%) belong to another category; most often it's geo but
also object or male/mname/furniture; cf. Results and Discussion regarding
stability of contrasts}
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
In/for the movie, We annotated different kinds of cinematographic cuts
\citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer in the depicted environment independent from the exact visual content in
the movie frame following the cut.

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    categories, annotation rules, and examples (given in English). The category
    \texttt{++} also contains adverbial of time.}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\todo[inline]{I revised part of motion correction/co-registration but as usually
I am pretty unsure about correctness}
\todo[inline]{what is missing: As I see it, AO must have been downsampled
to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm}

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
participant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AO stimulus.

@@

% my preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every stimulus segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AV analysis, we used all of the original 19
categories of descriptive nouns except \texttt{++}.
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories (see Table \ref{tab:ao-events}) that
served as experimental conditions.
% setting beats other category
Events that fell into one of the two setting-related category but also into
another category were treated as belonging to the setting-related category
(\texttt{se\_new} or \texttt{se\_old}).
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf ich den ganzen
Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories (see Table
\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not contain an
event of specific category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
movie cut and to another \texttt{no\_cut} event.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, and six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
found in Table \ref{tab:av-events}.
% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).
